Supplements for ``Tensor denoising and completion based on \\ ordinal observations''

### 2020-08-04 paper/Camera ready/supp.tex
clean up
corrected a typo

Let $d_{\text{total}}=\prod_{k\in[K]}d_k$, and $\gamma\in[0,1]$ be a constant to be specified later.  Our strategy is to construct a finite set of tensors $\tX=\{\Theta_i\colon i=1,\ldots \}\subset \tP$ satisfying the properties of (i)-(iv) in Lemma~\ref{lem:construction}. By Lemma~\ref{lem:construction}, such a subset of tensors exist. For any tensor  $\Theta\in\tX$, let $\mathbb{P}_{\Theta}$ denote the distribution of $\tY|\Theta$, where $\tY$ is the ordinal tensor. In particular, $\mathbb{P}_{\mathbf{0}}$ is the distribution of $\tY$ induced by the zero parameter tensor $\mathbf{0}$, i.e., the distribution of $\tY$ conditional on the parameter tensor $\Theta=\mathbf{0}$. Based on the Remark for Lemma~\ref{lem:KL}, we have
\begin{equation}\label{eq:KLbound1}
\mathrm{KL}(\mathbb{P}_{\Theta}|| \mathbb{P}_{\mathbf{0}})\leq C \FnormSize{}{\Theta}^2,
\end{equation}
where $C={(4L-6) \dot{f}^2(0)\over  A_\alpha}>0$ is a constant independent of the tensor dimension and rank.
Combining the inequality~\eqref{eq:KLbound1} with property (iii) of $\tX$, we have
\begin{equation}\label{eq:KLbound}
\text{KL}(\mathbb{P}_{\Theta}||\mathbb{P}_{\mathbf{0}})\leq \gamma^2 r_{\max} d_{\max}.
\end{equation}
From~\eqref{eq:KLbound} and the property (i), we deduce that the condition
\begin{equation}\label{eq:totalKL}
{1\over \text{Card}(\tX)-1}\sum_{\Theta \in\tX}\text{KL}(\mathbb{P}_{\Theta}, \mathbb{P}_{\mathbf{0}})\leq \varepsilon \log_2\left\{\text{Card}(\tX)-1 \right\}
\end{equation}
holds for any $ \varepsilon \geq 0$ when $\gamma\in[0,1]$ is chosen to be sufficiently small depending on $\varepsilon$, e.g., $\gamma \leq \sqrt{\varepsilon\log2\over8}$. By applying Lemma~\ref{lem:Tsybakov} to~\eqref{eq:totalKL}, and in view of the property (iv), we obtain that
\begin{equation}\label{eq:final}
\inf_{\hat \Theta}\sup_{\trueT\in \tX}\mathbb{P}\left(\FnormSize{}{\hat \Theta- \trueT}\geq  {\gamma\over 8} \min\left\{ \alpha\sqrt{d_{\text{total}}}, C^{-1/2}\sqrt{ r_{\max}d_{\max}}\right\} \right)\geq {1\over 2}\left(1-2\varepsilon-\sqrt{16 \varepsilon \over r_{\max}d_{\max}\log2}\right).
\end{equation}
Note that $\text{Loss}(\hat \Theta, \trueT)=\FnormSize{}{\hat \Theta- \trueT}^2/d_{\text{total}}$ and $\tX\subset \tP$. By taking $\varepsilon=1/10$ and $\gamma=1/11$, we conclude from~\eqref{eq:final} that
\begin{equation}\label{eq:prob}
\inf_{\hat \Theta}\sup_{\trueT\in \tP}\mathbb{P}\left(\text{Loss}(\hat \Theta, \trueT)\geq c\min\left \{ \alpha^2,  {C^{-1}r_{\max}d_{\max}\over d_{\text{total}}}\right \}\right)\geq {1\over 2}\left({4\over 5}- \sqrt{1.6\over r_{\max}d_{\max}\log2} \right)\geq {1\over 8},
\end{equation}
where $c = {1 \over 88^2}$ and the last inequality comes from the condition for $d_{\text{max}}$.
This completes the proof.
\end{proof}

>>>>

Let $d_{\text{total}}=\prod_{k\in[K]}d_k$, and $\gamma\in[0,1]$ be a constant to be specified later.  Our strategy is to construct a finite set of tensors $\tX=\{\Theta_i\colon i=1,\ldots \}\subset \tP$ satisfying the properties of (i)-(iv) in Lemma~\ref{lem:construction}. By Lemma~\ref{lem:construction}, such a subset of tensors exist. For any tensor  $\Theta\in\tX$, let $\mathbb{P}_{\Theta}$ denote the distribution of $\tY|\Theta$, where $\tY$ is the ordinal tensor. In particular, $\mathbb{P}_{\mathbf{0}}$ is the distribution of $\tY$ induced by the zero parameter tensor $\mathbf{0}$, i.e., the distribution of $\tY$ conditional on the parameter tensor $\Theta=\mathbf{0}$. Based on the Remark for Lemma~\ref{lem:KL}, we have
\begin{equation}\label{eq:KLbound1}
\mathrm{KL}(\mathbb{P}_{\Theta}|| \mathbb{P}_{\mathbf{0}})\leq C \FnormSize{}{\Theta}^2,
\end{equation}
where $C={(4L-6) \dot{f}^2(0)\over  A_\alpha}>0$ is a constant independent of the tensor dimension and rank.
Combining the inequality~\eqref{eq:KLbound1} with property (iii) of $\tX$, we have
\begin{equation}\label{eq:KLbound}
\text{KL}(\mathbb{P}_{\Theta}||\mathbb{P}_{\mathbf{0}})\leq \gamma^2 r_{\max} d_{\max}.
\end{equation}
From~\eqref{eq:KLbound} and the property (i), we deduce that the condition
\begin{equation}\label{eq:totalKL}
{1\over \text{Card}(\tX)-1}\sum_{\Theta \in\tX}\text{KL}(\mathbb{P}_{\Theta}, \mathbb{P}_{\mathbf{0}})\leq \varepsilon \log\left\{\text{Card}(\tX)-1 \right\}
\end{equation}
holds for any $ \varepsilon \geq 0$ when $\gamma\in[0,1]$ is chosen to be sufficiently small depending on $\varepsilon$, e.g., $\gamma \leq \sqrt{\varepsilon\log2\over8}$. By applying Lemma~\ref{lem:Tsybakov} to~\eqref{eq:totalKL}, and in view of the property (iv), we obtain that
\begin{equation}\label{eq:final}
\inf_{\hat \Theta}\sup_{\trueT\in \tX}\mathbb{P}\left(\FnormSize{}{\hat \Theta- \trueT}\geq  {\gamma\over 8} \min\left\{ \alpha\sqrt{d_{\text{total}}}, C^{-1/2}\sqrt{ r_{\max}d_{\max}}\right\} \right)\geq {1\over 2}\left(1-2\varepsilon-\sqrt{16 \varepsilon \over r_{\max}d_{\max}\log2}\right).
\end{equation}
Note that $\text{Loss}(\hat \Theta, \trueT)=\FnormSize{}{\hat \Theta- \trueT}^2/d_{\text{total}}$ and $\tX\subset \tP$. By taking $\varepsilon=1/10$ and $\gamma=1/11$, we conclude from~\eqref{eq:final} that
\begin{equation}\label{eq:prob}
\inf_{\hat \Theta}\sup_{\trueT\in \tP}\mathbb{P}\left(\text{Loss}(\hat \Theta, \trueT)\geq c\min\left \{ \alpha^2,  {C^{-1}r_{\max}d_{\max}\over d_{\text{total}}}\right \}\right)\geq {1\over 2}\left({4\over 5}- \sqrt{1.6\over r_{\max}d_{\max}\log2} \right)\geq {1\over 8},
\end{equation}
where $c = {1 \over 88^2}$ and the last inequality comes from the condition for $d_{\text{max}}$.
This completes the proof.
\end{proof}
